---
title: "Alcohol vs Seat choice"
author: "John G"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The fancy notch boxplot communicates based off of the median that the average amount of drinks that somebody in the back is taking is bigger than somebody who is in the front and middle.     

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

There is a statistical difference in the back and the front and middle.  

## Inferential Tests

## Conclusions


